---
title: "Lab 10: Multiple Regression"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #Always do this.

```

### Introduction

We will continue our analysis of the fictitious company that’s trying to determine how much
money to spend on various types of advertising for the coming year. If you don’t have your data
file ”media spend.csv” from the last lab in your working directory, download it from Brightspace.

## Question 1

```{r}

#(a) Load the media spend.csv dataset into R and save it to spend.
spend = read.csv("media_spend.csv")

#(b) Install and load GGally package

#install.packages("GGally")    # only run once
library(GGally)

#(c)  Produce a correlation matrix of all variables using the command ggpairs(parameters).
#     Since we want to show all variables in the spend data frame, we can input spend as the
#     parameter.
ggpairs(spend, title = "Correlation Matrix of Media")

#(d)  Which pair(s) of independent variables showed significant correlation (+ or -)?

# Answer: The pair newspaper & Radio have a significant correlation which is positive (+)


```

## Question 2

```{r}

#(a) Perform a multiple regression using all three types of advertising vs the 
#    response variable, Sales. Save the results and name it full_model. Print out
#    the summary of the regression.
full_model = lm(formula = Sales ~ TV + Radio + Newspaper, data = spend)
summary(full_model)

#(b) Compare and comment on the slope coefficients of the explanatory variables and their
#    corresponding p-values with those obtained from your previous lab when you performed
#    linear regressions on individual explanatory variables.

# Here are values from the previous from last lab.

slope_vec <- c(0.055465, 0.1244, 0.03832)
names(slope_vec) <- c("TV", "Radio", "Newspaper")

p_vec <- c(2.2e-16, 3.88e-07, 0.02549)
names(p_vec) <- c("TV", "Radio", "Newspaper")

# The slope coefficients for TV  are close.
# The slope coefficients for Radio are not close.
# The slope coefficients for Newspaper are very different.

# The p-values for TV and radio are very small for both analysis.
# The p-value for Newspaper is significant individually, but not significant if it is a part of multiple regression model.  

# Note: Once you introduce a multiple regression model, the number in the
# individual regression analysis should be only used for comparison purpose.

# (c) Which of the regressor(s) is(are) not statistically significant in the full model?
#     Explain how you know they are not significant.

# Answer: The regressor Newspaper is not significant because it's p-value is (0.954) which is greater than 0.05.

```

## Question 3

```{r}

# Optional: You can "clean up" your correlation by skipping variables you
# don't want to use.

# Uncomment it if you want to see the output.

ggpairs(subset(spend, select = c("TV", "Radio", "Sales")))

# The subset subset command includes the variables you specify.

# (a) Run a multiple regression with only the regressors that are significant 
#     in full model and name it new model. Print out the summary.
new_model = lm(formula = Sales ~ TV + Radio, data = spend)
summary(new_model)
#(b) Are there any insignificant regressors in this model?

# Answer: There are no insignificant regressors in this model.


#(c) Now you have two regression models: full_model and new_model. Which one will you
#    select as the final (better) regression model. Justify your choice.

# Answer: I will choose the new model as it contains only the significant regressors.


#(d) Write out the equation for new_model.

# Answer: y = 4.630879 + 0.054449*(TV) + 0.107175*(Radio)

# Recall The unit for Sales is millions of dollars and the units for TV, Radio, 
# and Newspaper are in thousands of dollars. 

#(e) Use new_model to predict sales if the company spends $200,000 in TV ad and 
#    $30,000 in radio ad. Is this prediction a good one for this model? Why or 
#    why not?
y = 4.630879 + 0.054449*(200) + 0.107175*(30)
y

cat("The predicted sales is", y,"Millon Dollars")
summary(spend$TV)
summary(spend$Radio)

# The x values are within the range of the data we obtained and hence, the model will give us a good prediction.  

#(f) Use new_model to predict sales if the company spends $500,000 in TV ad and 
#    $80,000 in radio ad. Is this prediction a good one for this model? Why or 
#    why not?
y1 = 4.630879 + 0.054449*(500) + 0.107175*(80)
y1

cat("The predicted sales is", y1, "Million Dollars")
# The x values are outside the range of the data we obtained hence, the prediction is nnot relaible.

```
### Knit this file. 

### Open the html file in your browser.

### Print that file as a pdf file.

### Submit the pdf file to Brightspace.

## End of Lab 10.

