---
title: "Lab 3"
author: "Sahil Sanghvi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## 1.

    Download the data set inflation_consumer.csv posted under Lab Content in 
    Brightspace (under Lab 3) and save it to whatever directory you are using for this 
    course. 
(a) Read the inflation_consumer file into R and call it Inflation.df. Optional: Show a few observations.
(b) How many observations (rows) are in this dataset? How many variables (columns)? 
(c) What are the mean values for the Year column? Does this value mean anything?
(d) Determine which country has the lowest inflation and the corresponding year. 
(e) Determine which country has the highest inflation and the corresponding year.

```{r}

#1a
#Inflation.df = read.csv("inflation_consumer.csv")

Inflation.df = read.csv(file.choose(),header = TRUE)

head(Inflation.df)

#1b

nrow(Inflation.df)
ncol(Inflation.df)
dim(Inflation.df)

#Make sure not to count column(s) that is(are) identifier(s).

#1c

mean(Inflation.df$Year)
range(Inflation.df$Year)
table(Inflation.df$Year)


#1d

minimum_index <- which.min(Inflation.df$Inflation)
min(Inflation.df$Inflation)

Inflation.df[which.min(Inflation.df$Inflation),c("Country","Year")]

country_with_lowest_inflation <- Inflation.df$Country[minimum_index]

year_with_lowest_inflation <- Inflation.df$Year[minimum_index]

country_with_lowest_inflation

year_with_lowest_inflation

#1e


maximum_index <- which.max(Inflation.df$Inflation)
max(Inflation.df$Inflation)

max_year_country <- Inflation.df[maximum_index,c("Year","Country")]

country_with_highest_inflation <- Inflation.df$Country[maximum_index]

year_with_highest_inflation <- Inflation.df$Year[maximum_index]

country_with_highest_inflation

year_with_highest_inflation


```

## 2. 

(a) Create a new data frame that contains all countries with inflation over 7.00 and save it
    to Sub_Inflation.

(b) Determine the average of the inflation column and save this to a variable called avg.inflation.

(c) Use Sub_Inflation to determine the number of country counts with inflation over 12.00
    and print out the value.

(d) Create a vector named Inflation Status which contains two levels: High and Low. All
    countries in Sub_Inflation with inflation over 12.00 should be labeled as High, otherwise
    named as Low.

(e) Use the Inflation_Status vector to print out the number of country counts with
    inflation over that 12.00. This number should be the same as in part (c).
    
```{r}

#2a
Sub_Inflation = Inflation.df[Inflation.df$Inflation > 7, ]

Sub_Inflation1 = subset(Inflation.df, Inflation.df$Inflation > 7)

identical(Sub_Inflation,Sub_Inflation1)


#2b

avg.inflation = mean(Sub_Inflation$Inflation)

avg.inflation
#2c

(Sub_Inflation$Inflation > 12)
num_countries_over_12 <- sum(Sub_Inflation$Inflation > 12)

num_countries_over_12

#Type "?subset" in Rstudio to find out what subset() command does.


#2d

#Approach 1

Sub_Inflation$Status[Sub_Inflation$Inflation > 12] = "High"
Sub_Inflation$Status[Sub_Inflation$Inflation <= 12] = "Low"


#Approach 2

Sub_Inflation$Status = "High"
Sub_Inflation$Status [Sub_Inflation$Inflation <= 12] = "Low"


#The following commands create a variable "Status" in the Sub_Inflation data frame
#with the required information



#2e
Inflation_Status = (Sub_Inflation$Status == "High")
head(Inflation_Status)
sum(Inflation_Status)

```

