---
title: "Assignment 2"
author: "Sahil Sanghvi"
date: "2024-02-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

Download the data sets Superstores.csv and save them to whatever directory you are using
for this course. Load the tidyverse package. This will load both dplyr and ggplot2 packages.
Read in the file and save it as a data frame super. This data set contents information about
customer orders. Take a look at the data frame to familiarize yourself with its contents. It
is a typical data set with lots of variables. Note that the column ”Row ID” is not a variable.
It’s an identifier, or an index.

```{r}

# Load necessary libraries
library(tidyverse)

# 1. Read the Superstores.csv file and save it as a data frame 'super'
super <- read.csv("Superstores.csv")

# Check the structure of the dataframe
str(super)

# (a) Total Sales for the Category "Office Supplies"
office_supplies_sales <- super %>%
  filter(Category == "Office Supplies") %>%
  summarise(total_sales = sum(Sales))

print(office_supplies_sales)

# (b) Create a new data frame containing only orders for California
superCali <- super %>%
  filter(State == "California")

# Show a few observations from superCali
head(superCali)

# (c) Bar graph of order counts by Regions
order_counts_by_region <- super %>%
  group_by(Region) %>%
  summarise(order_count = n())

# Basic bar graph
ggplot(order_counts_by_region, aes(x = Region, y = order_count, fill = Region)) +
  geom_bar(stat = "identity") +
  labs(title = "Order Counts by Region") +
  theme_minimal()


```

## Question 2
The following question deals with the data set Government expenditure per student.csv, which
you will need to download from the Brightspace assignment page.

```{r}

# Load necessary libraries
library(ggplot2)

# 1. Read the "Government expenditure per student.csv" file
gov_exp_per_student <- read.csv("Government_expenditure_per_student.csv")

# (a) Create a histogram displaying the distribution of the variable Value

ggplot(gov_exp_per_student, aes(x = Value, fill = "")) + 
  geom_histogram(fill = "green",color = "black") + 
  ggtitle("Goverment Expense Per Students") +
  labs(x ="Expense", y = "No.Of.Countries") 

# (b) Describe the shape of the distribution
# Determine whether the distribution is symmetric, left-skewed, or right-skewed based on the histogram plot.

cat("The distribution is right skewed")

# (c) Compute the appropriate center value and corresponding measures of variability
# You can compute the mean, median, and standard deviation to describe the center and spread of the distribution.

ggplot(gov_exp_per_student, aes(x = Value, fill = "")) + 
  geom_histogram(fill = "green",color = "black") + 
  ggtitle("Goverment Expense Per Students") +
  labs(x ="Expense", y = "No.Of.Countries") + 
  geom_vline(xintercept = median(gov_exp_per_student$Value), linetype = "dashed", size = 2.0)


# (d) Compute the trimmed mean of the data
trimmed_mean <- mean(gov_exp_per_student$Value, trim = 0.05)
trimmed_mean


```

## Question 3

During lecture, I mentioned that there is no ”geom pie” command in ggplot2 to product a
pie chart. However, there is a way to acheive that. Use your research skill, find out how and
use the data set from the file ”rawgrades.csv” in the ”Skeleton Notes” folder to generate a
pie chart. Your pie chart should have the following:

(a) A title;
(b) A label for each category;
(c) Different colours for different pies;
(d) The percentage for each category.


```{r}

# Load necessary libraries
library(ggplot2)

# Read the data
rawgrades <- read.csv("rawgrades.csv")

# Create a summary of grades
grades_summary <- table(rawgrades$Grade)

# Convert summary to data frame
grades_summary_df <- as.data.frame(grades_summary)
colnames(grades_summary_df) <- c("Grade", "Count")

# Calculate percentage
grades_summary_df$Percentage <- grades_summary_df$Count / sum(grades_summary_df$Count) * 100

# Create a pie chart (Without pertentages in piechart)
pie_chart <- ggplot(grades_summary_df, aes(x = "", y = Percentage, fill = Grade)) +
  geom_bar(stat = "identity") +
  coord_polar(theta = "y") +
  labs(title = "Distribution of Grades",
       fill = "Grade",
       y = "Percentage") +
  theme_minimal() +
  theme(legend.position = "bottom")

# pie chart (With pertentages in piechart)
grades_summary_df %>%
  mutate(perc =scales::percent(Count/sum(Count))) %>%
  arrange(desc(Grade)) %>%
  mutate(pos = cumsum(Count)- Count/2) %>%
  ggplot(aes(x = "", y = Count, fill = factor(Grade) )) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  ggrepel::geom_label_repel(aes(x = "", y = pos, label = perc), size=5, show.legend = F, nudge_x = 1) +
  guides(fill = guide_legend(title = "Group"))

# Display the pie chart
print(pie_chart)

```



