---
title: "Lab 9"
author: "Sahil Sanghvi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```

### Introduction

Download the data set media_spend.csv and save it to whatever directory you are using for this course.

Today’s dataset contains information about a fictitious company that’s trying to determine how much money to spend on various types of advertising for the coming year. They have historical data showing sales (in millions of dollars) and the amount they spent on TV, Radio, and Newspaper advertising that year (in thousands of dollars). Our goal today is to determine which types of advertising effects sales the most.

## Question 1

```{r}

#(a) Load the media spend.csv dataset into R and save it to spend.
spend = read.csv("media_spend.csv")

#(b) We are trying to see how the advertising effects sales, therefore, sales is our response variable and the other columns are our regressors. List the regressors (independent variables).
colnames(spend)
# TV, Radio and Newspaper are the regressors.

#(c) Plot the response variable (as the y-axis) against each of the regressor variables (one plot for each regressor) using ggplot2. Display the three plots side by side using the "gridExtra" package.

#install.packages("gridExtra")              # install package if needed
library(gridExtra)                        # Load gridExtra package
library(ggplot2)
plot1 = ggplot(spend, aes(x = TV, y = Sales)) +
  geom_point(shape = 1) + labs(x = "TV Ads", y = "Sales") + 
  ggtitle("Sales while Advertizing through TV")

plot2 = ggplot(spend, aes(x = Radio, y = Sales)) +
  geom_point(shape = 2) + labs(x = "Radio Ads", y = "Sales") + 
  ggtitle("Sales while Advertizing through Radio")

plot3 = ggplot(spend, aes(x = Newspaper, y = Sales)) +
  geom_point(shape = 3) + labs(x = "Newspaper Ads", y = "Sales") + 
  ggtitle("Sales while Advertizing through Newspaper")

grid.arrange(plot1, plot2, plot3, ncol = 3)

# Method 2
regressor = c("TV","Radio","Newspaper")
plots = list()
for (ii in 1:length(regressor)){
  plots[[ii]] = ggplot(spend, aes_string(x = regressor[ii], y = "Sales")) +
    geom_point(shape = ii)
}
grid.arrange(plots[[1]],plots[[2]],plots[[3]], ncol = 3)

#(d) Looking only at the plots, which type of advertising do you think will have the largest effect on sales?
# It is hard to tell from the plots, we need further analysis. Even the x ranges of all the graphs are different

```

## Question 2

```{r}

#(a) Perform a linear regression for each form of advertising vs the response variable, sales. Print out the summary for each of these regressions and take note of the p-value for the t-test on the significance of the coefficient for each.
options(scipen = 999)
SalesbyTV = lm(spend$Sales ~ spend$TV)
summary(SalesbyTV)

SalesbyRadio = lm(spend$Sales ~ spend$Radio)
summary(SalesbyRadio)

SalesbyNewspaper = lm(spend$Sales ~ spend$Newspaper)
summary(SalesbyNewspaper)


#(b) Which of the regressors is the most significant in terms of the p-value?
# Regressor TV because lowest p-value

#(c) Of all the significant regressors, which one has the biggest impact on sales on its own?
# The largest estimate is of regressor Radio because of the larger slope or coefficient (Beta).

#(d) Create a vector of the p-values and name each element with the corresponding type of advertising.
p_vec = c(2.2e-16,3.88e-07, 0.02549)
names(p_vec) = c("TV","Radio","Newspaper")

#(e) Create another vector of the slope coefficients and name each element with the corresponding type of advertising.
slope_vec = c(0.055465,0.1244,0.03832)
names(slope_vec) = c("TV","Radio","Newspaper")

#(f) Display both vectors.
p_vec
slope_vec

# Method 2
p_vec2 = c()
slope_vec2 = c()

variable = "TV"
for (variable in regressor){
  formula = as.formula(paste("Sales~",variable))
  model = lm(formula, data = spend)
  
  cat("summary for model: Sales ~", variable,"\n")
  print(summary(model))
  cat("\n\n")

  p_vec2 = c(p_vec2, summary(model)$coefficients[2,4])
  slope_vec2 = c(slope_vec2, coef(model)[2])
}

names(p_vec2) = regressor
names(slope_vec2) = regressor

p_vec2
slope_vec2
```

## End of Lab 9.